---
title: "Flex Dashboard"
author: "Maddie Banyas"
date: "10/20/2021"
output: 
    flexdashboard::flex_dashboard:
    orientation: columns 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)

#package initialization
rm(list = ls()) # clear global environment
graphics.off() # close all graphics
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(DataExplorer,tidyverse,readxl,zoo,stargazer,kableExtra,skimr,plotly,ggpubr,vtable,tm, flexdashboard, fontawesome)

#load data
data=readRDS("FSB_BI_Survey_2019_2021.rds")
```

Insights {data-orientation=columns}
=================================================================

## Overview of the Data

### type text here

## Insights

### type text here

## Recommendations


Page 2: Survey Overview {data-orientation=columns}
=================================================================

Overview of Survey responses 

column {data-width = 300}
-----------------------------------------------------------------

### Response Rate

```{r}

```


### Responses by Primary Major

```{r}

```

column {data-width = 700}
-----------------------------------------------------------------

### Placement Status

```{r}

```

Page 3: Major Breakdown {data-orientation=columns}
=================================================================

column {data-width = 500}
-----------------------------------------------------------------

### Placement Rate by Major

```{r}

```

column {data-width = 500}
-----------------------------------------------------------------

### Salary by Major

```{r}

```


Page 4: Geographic Breakdown {data-orientation=columns}
=================================================================

column {data-width = 500}
-----------------------------------------------------------------

### Where each majors are going

```{r}

```

column {data-width = 500}
-----------------------------------------------------------------

### The four Cs

```{r}

```

Page 5: Trends {data-orientation=columns}
=================================================================

column {data-width = 500}
-----------------------------------------------------------------

### Salary Trends by Major

```{r}

```

column {data-width = 500}
-----------------------------------------------------------------

### Salary Trends by Gender

```{r}

```


Page 6: Attributes{data-orientation=columns}
=================================================================

column {data-width = 500}
-----------------------------------------------------------------

### GPA

```{r}

```

column {data-width = 500}
-----------------------------------------------------------------

### Graph Number 2

Page 7: School Comparisons {data-orientation=columns}
=================================================================

column {data-width = 500}
-----------------------------------------------------------------

### Compare Placement rates

```{r}

```


column {data-width = 500}
-----------------------------------------------------------------

### Compare starting salary 

```{r}

```

