---
title: "Cleaning the Combined BI And Survey Career Data"
author: "Group 1"
output:
  html_document:
    date: "`r format(Sys.time(), '%d %B, %Y')`"
    code_folding: hide
    df_print: paged
    theme: cerulean
    toc: yes
    toc_float: yes
    code_download: true
  word_document:
    toc: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)

#package intialization
rm(list = ls()) # clear global environment
graphics.off() # close all graphics
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(DataExplorer,tidyverse,readxl,zoo,stargazer,kableExtra,skimr,plotly,ggpubr,vtable,tm)
```


## Read in the data

```{r}
data=readRDS(file = "FSB_BI_Survey_2019_2021.rds")
```

## Replace Certain Responses with NA in Various Columns

```{r}
library(naniar)
data<- data %>%
replace_with_na(replace = list(major2 = c("none")))
	
data<- data %>%
replace_with_na(replace = list(minor1 = c("No Minor")))
	
data<- data %>%
replace_with_na(replace = list(minor2 = c("No Minor")))
	
data<- data %>%
replace_with_na(replace = list(latin_honors = c("0")))
	
data<- data %>%
replace_with_na(replace = list(survey_city = c("N/A","na","NA")))
	
data<- data %>%
replace_with_na(replace = list(survey_company = c("TBD","Not yet","NA","na","N/A","*startup that cannot be named")))
```

## Remove Repeated Responses from the Data Set

```{r}
data[duplicated(data),]
data = distinct(data)
```

# Data Preprocessing

Describing each data preprocessing step with small chunks of code, output where necessary, and documentation

## Recode Bianary Variables as Factors

```{r}
data$BBRJ <- as.factor(data$BBRJ)
data$`Business Direct Admit` <- as.factor(data$`Business Direct Admit`)
data$`Combined Bacc and Masters` <- as.factor(data$`Combined Bacc and Masters`)
data$`Dean's List` <- as.factor(data$`Dean's List`)
data$`First Generation College Stdnt` <- as.factor(data$`First Generation College Stdnt`)
data$`FSB Scholars` <- as.factor(data$`FSB Scholars`)
data$`Honors Program` <- as.factor(data$`Honors Program`)
data$`President's List` <- as.factor(data$`President's List`)
data$`Study Abroad Courtesy Account` <- as.factor(data$`Study Abroad Courtesy Account`)
data$`Transfer Work (Pre-Banner)` <- as.factor(data$`Transfer Work (Pre-Banner)`)
data$`Cum Laude` <- as.factor(data$`Cum Laude`)
data$`Magna Cum Laude` <- as.factor(data$`Magna Cum Laude`)
data$`Summa Cum Laude` <- as.factor(data$`Summa Cum Laude`)
data$`University Honors` <- as.factor(data$`University Honors`)
data$`UniversityHonors w/Distinction` <- as.factor(data$`UniversityHonors w/Distinction`)
```

## Clean Survey_State Variable

```{r}
data$survey_state = gsub("Ohio","OH", data$survey_state)
data$survey_state = gsub("Ohio / USA","OH", data$survey_state)
data$survey_state = gsub("new york","NY", data$survey_state)
data$survey_state = gsub("Ohio, USA","OH", data$survey_state)
data$survey_state = gsub("Illinois","IL", data$survey_state)
data$survey_state = gsub("D.C.","DC", data$survey_state)
data$survey_state = gsub("Michigan, Detroit","MI", data$survey_state)
data$survey_state = gsub("Indiana","IN", data$survey_state)
data$survey_state = gsub("Minnesota","MN", data$survey_state)
data$survey_state = gsub("Washington D.C/United States","DC", data$survey_state)
data$survey_state = gsub("Pennsylvania","PA", data$survey_state)
data$survey_state = gsub("IL/USA","IL", data$survey_state)
data$survey_state = gsub("OH/USA","OH", data$survey_state)
data$survey_state = gsub("North Carolina","NC", data$survey_state)
data$survey_state = gsub("Washington","WA", data$survey_state)
data$survey_state = gsub("Georgia, USA","GA", data$survey_state)
data$survey_state = gsub("Massachusetts, USA","MA", data$survey_state)
data$survey_state = gsub("TBA / USA","", data$survey_state)
data$survey_state = gsub("Florida","FL", data$survey_state)
data$survey_state = gsub("Fujian Province","", data$survey_state)
data$survey_state = gsub("California","CA", data$survey_state)
data$survey_state = gsub("Ohio/United States","OH", data$survey_state)
data$survey_state = gsub("Wisconsin","WI", data$survey_state)
data$survey_state = gsub("Illinois / USA","IL", data$survey_state)
data$survey_state = gsub("Montana","MT", data$survey_state)
data$survey_state = gsub("MI / U.S.","MI", data$survey_state)
data$survey_state = gsub("Kansas","KS", data$survey_state)
data$survey_state = gsub("Ohio / The United States","OH", data$survey_state)
data$survey_state = gsub("Georgia","GA", data$survey_state)
data$survey_state = gsub("New York","NY", data$survey_state)
data$survey_state = gsub("IL, USA","IL", data$survey_state)
data$survey_state = gsub("OH/Us","OH", data$survey_state)
data$survey_state = gsub("TBD","", data$survey_state)
data$survey_state = gsub("Virginia/ USA","VA", data$survey_state)
data$survey_state = gsub("Texas","TX", data$survey_state)
data$survey_state = gsub("Virginia (VA)","VA", data$survey_state)
data$survey_state = gsub("Virginia/ USA","VA", data$survey_state)
data$survey_state = gsub("India","", data$survey_state)
data$survey_state = gsub("Rhode Island","RI", data$survey_state)
data$survey_state = gsub("Zhejiang Province","", data$survey_state)
data$survey_state = gsub("China","", data$survey_state)
data$survey_state = gsub("MA / USA","MA", data$survey_state)
data$survey_state = gsub("USA","", data$survey_state)
data$survey_state = gsub("Colorado","CO", data$survey_state)
data$survey_state = gsub("Zhejiang Province","", data$survey_state)
data$survey_state = gsub("IN / USA","IN", data$survey_state)
data$survey_state = gsub("Ireland","", data$survey_state)
data$survey_state = gsub("India","", data$survey_state)
data$survey_state = gsub("Ohio/United States","OH", data$survey_state)
data$survey_state = gsub("Colorado/ United States","CO", data$survey_state)
data$survey_state = gsub("OHIO","OH", data$survey_state)
data$survey_state = gsub("New York, USA","NY", data$survey_state)
data$survey_state = gsub("iL","IL", data$survey_state)
data$survey_state = gsub("Ohio / United States","", data$survey_state)
data$survey_state = gsub("TBA / USA","", data$survey_state)
data$survey_state = gsub("Michigan","MI", data$survey_state)
data$survey_state = gsub("Kentucky","KY", data$survey_state)
data$survey_state = gsub("IL, US","IL", data$survey_state)
data$survey_state = gsub("ohio","OH", data$survey_state)
data$survey_state = gsub("Belize","BZ", data$survey_state)
data$survey_state = gsub("Wisconsin / USA","WI", data$survey_state)
data$survey_state = gsub("oh","OH", data$survey_state)
data$survey_state = gsub("New york","NY", data$survey_state)
data$survey_state = gsub("Oregon","OR", data$survey_state)
data$survey_state = gsub("Connecticut","CT", data$survey_state)
data$survey_state = gsub("MI / U.S.","MI", data$survey_state)
data$survey_state = gsub("District of Columbia","DC", data$survey_state)
data$survey_state = gsub("Connecticut","CT", data$survey_state)
data$survey_state = gsub("United Kingdom","UK", data$survey_state)
data$survey_state = gsub("Turkey","TR", data$survey_state)
data$survey_state = gsub("Tennessee","TN", data$survey_state)
data$survey_state = gsub("Nebraska","NE", data$survey_state)
data$survey_state = gsub("Illinois/ US","TR", data$survey_state)
data$survey_state = gsub("illinois","IL", data$survey_state)
data$survey_state = gsub("Canada","", data$survey_state)
data$survey_state = gsub("Delaware","DE", data$survey_state)
data$survey_state = gsub("CO/ United States","CO", data$survey_state)
data$survey_state = gsub("IL, United States","IL", data$survey_state)
data$survey_state = gsub("IL / ","IL", data$survey_state)
data$survey_state = gsub("IN / ","IN", data$survey_state)
data$survey_state = gsub("IL/ ","IL", data$survey_state)
data$survey_state = gsub("IL/ US","IL", data$survey_state)
data$survey_state = gsub("Maine","ME", data$survey_state)
data$survey_state = gsub("NY,","NY", data$survey_state)
data$survey_state = gsub("OH / ","OH", data$survey_state)
data$survey_state = gsub("OH / The United States","OH", data$survey_state)
data$survey_state = gsub("OH / United States","OH", data$survey_state)
data$survey_state = gsub("OH,","OH", data$survey_state)
data$survey_state = gsub("OH/ United States","OH", data$survey_state)
data$survey_state = gsub("OH/United States","OH", data$survey_state)
data$survey_state = gsub("Virginia (VA)","VA", data$survey_state)
data$survey_state = gsub("Virginia","VA", data$survey_state)
data$survey_state = gsub("TX/ ","TX", data$survey_state)
data$survey_state = gsub("WI / ","WI", data$survey_state)
data$survey_state = gsub("WA DCUnited States","DC", data$survey_state)
data$survey_state = gsub("ILUS","IL", data$survey_state)
data$survey_state = gsub("Il","IL", data$survey_state)
data$survey_state = gsub("OHThe United States","OH", data$survey_state)
data$survey_state = gsub("OHUnited States","OH", data$survey_state)
data$survey_state = gsub(" TX/","TX", data$survey_state)
data$survey_state = gsub("VA (VA)","VA", data$survey_state)
data$survey_state = gsub("VA (VA) ","VA", data$survey_state)
data$survey_state = gsub(" VA (VA)","VA", data$survey_state)
data$survey_state = gsub(" VA (VA) ","VA", data$survey_state)
data$survey_state = gsub("TX/","TX", data$survey_state)
data$survey_state = gsub("Montenegro","", data$survey_state)
data$survey_state = gsub("United States","US", data$survey_state)
```

```{r}
data$survey_state[data$survey_state == "VA (VA)"] <- "VA"
data$survey_state[data$survey_state == "Remote"] <- "Other"
data$survey_state[data$survey_state == "N/A"] <- "Other"
data$survey_state[data$survey_state == "na"] <- "Other"
data$survey_state[data$survey_state == "NA"] <- "Other"
```

## Clean Survey_City Variable

```{r}
data$survey_city[data$survey_city == "Witchita"] <- "Wichita"
data$survey_city[data$survey_city == "Westerville (Columbus)"] <- "Westerville"
data$survey_city[data$survey_city == "Washington D.C"] <- "D.C."
data$survey_city[data$survey_city == "Washington DC"] <- "D.C."
data$survey_city[data$survey_city == "Washington, D.C."] <- "D.C"
data$survey_city[data$survey_city == "Washington"] <- "D.C."
data$survey_city[data$survey_city == "Washinton"] <- "D.C."
data$survey_city[data$survey_city == "Tyson"] <- "Tysons"
data$survey_city[data$survey_city == "Tysons Corner"] <- "Tysons"
data$survey_city[data$survey_city == "San francisco"] <- "San Francisco"
data$survey_city[data$survey_city == "Phoneix"] <- "Phoenix"
data$survey_city[data$survey_city == "Philadephia"] <- "Philadelphia"
data$survey_city[data$survey_city == "Oakbrook"] <- "Oak Brook"
data$survey_city[data$survey_city == "NYC"] <- "New York"
data$survey_city[data$survey_city == "New york"] <- "New York"
data$survey_city[data$survey_city == "new york"] <- "New York"
data$survey_city[data$survey_city == "Manhattan"] <- "New York"
data$survey_city[data$survey_city == "Milwaukwee"] <- "Milwaukee"
data$survey_city[data$survey_city == "LosAngeles"] <- "Los Angeles"
data$survey_city[data$survey_city == "Jersey city"] <- "Jersey City"
data$survey_city[data$survey_city == "Indianpolis"] <- "Indianapolis"
data$survey_city[data$survey_city == "indianapolis"] <- "Indianapolis"
data$survey_city[data$survey_city == "Hamiliton"] <- "Hamilton"
data$survey_city[data$survey_city == "grand rapids"] <- "Grand Rapids"
data$survey_city[data$survey_city == "Ft Myers"] <- "Ft. Myers"
data$survey_city[data$survey_city == "Fort Myers"] <- "Ft. Myers"
data$survey_city[data$survey_city == "Forth Worth"] <- "Fort Worth"
data$survey_city[data$survey_city == "Findlay (Tentative)"] <- "Findlay"
data$survey_city[data$survey_city == "Findley"] <- "Findlay"
data$survey_city[data$survey_city == "Don't Know Yet"] <- "TBD"
data$survey_city[data$survey_city == "Colubmus"] <- "Columbus"
data$survey_city[data$survey_city == "CLEVELAND"] <- "Cleveland"
data$survey_city[data$survey_city == "cleveland"] <- "Cleveland"
data$survey_city[data$survey_city == "Cincinnnati"] <- "Cincinnati"
data$survey_city[data$survey_city == "Cincinnati, OH"] <- "Cincinnati"
data$survey_city[data$survey_city == "Cincinatti"] <- "Cincinnati"
data$survey_city[data$survey_city == "chicago"] <- "Chicago"
data$survey_city[data$survey_city == "buffalo grove"] <- "Buffalo Grove"
data$survey_city[data$survey_city == "Brooklyn"] <- "New York"
data$survey_city[data$survey_city == "boston"] <- "Boston"
data$survey_city[data$survey_city == "Blue ash"] <- "Blue Ash"
data$survey_city[data$survey_city == "Istanbul"] <- "International"
data$survey_city[data$survey_city == "Zhejiang"] <- "International"
data$survey_city[data$survey_city == "Xiamem"] <- "International"
data$survey_city[data$survey_city == "Warsaw"] <- "International"
data$survey_city[data$survey_city == "Tampa Bay"] <- "Tampa"
data$survey_city[data$survey_city == "Shanghai"] <- "International"
data$survey_city[data$survey_city == "QingDao"] <- "International"
data$survey_city[data$survey_city == "Podgorica"] <- "International"
data$survey_city[data$survey_city == "New York City"] <- "New York"
data$survey_city[data$survey_city == "New York CIty"] <- "New York"
data$survey_city[data$survey_city == "Indiana"] <- "Indianapolis"
data$survey_city[data$survey_city == "Indiana"] <- "Indianapolis"
data$survey_city[data$survey_city == "Brooklyn Heights"] <- "New York"
data$survey_city[data$survey_city == "Bengaluru"] <- "International"
data$survey_city[data$survey_city == "D.C"] <- "D.C."
data$survey_city[data$survey_city == "Hangzhou"] <- "International"
data$survey_city[data$survey_city == "North Canton, Ohio"] <- "Canton"
data$survey_city[data$survey_city == "North Canton, Ohio"] <- "Canton"
data$survey_city[data$survey_city == "Placencia"] <- "International"
data$survey_city[data$survey_city == "Podgorica"] <- "International"
data$survey_city[data$survey_city == "Redwood Shores"] <- "Redwood City"
data$survey_city[data$survey_city == "Saint Petersburg"] <- "St Petersburg"
data$survey_city[data$survey_city == "Saint Petersburg"] <- "St Petersburg"
```

## Clean Survey_Company Variable

```{r}
data$survey_company[data$survey_company== "Worldpay from FIS"] <- "Worldpay"
data$survey_company[data$survey_company== "Worldpay/Fidelity Investment"] <- "Worldpay"
data$survey_company[data$survey_company== "William Blair & Company"] <- "William Blair"
data$survey_company[data$survey_company== "Welltower"] <- "Welltower Inc."
data$survey_company[data$survey_company== "Wabtec/GE Transportation"] <- "Wabtec"
data$survey_company[data$survey_company== "WW Grainger"] <- "W.W. Grainger"
data$survey_company[data$survey_company== "VMLY&R"] <- "VMLY&R Commerce"
data$survey_company[data$survey_company== "U.S Bank"] <- "U.S. Bank"
data$survey_company[data$survey_company== "TQL"] <- "Total Quality Logistics"
data$survey_company[data$survey_company== "TJX Companies"] <- "The TJX Companies"
data$survey_company[data$survey_company== "The David J Joseph Company"] <- "The David J. Joseph Company"
data$survey_company[data$survey_company== "The Cincinnati Insurance Companies"] <- "The Cincinnati Insurance Company"
data$survey_company[data$survey_company== "Terrilium"] <- "Terillium"
data$survey_company[data$survey_company== "Stryker"] <- "Stryker Corporation"
data$survey_company[data$survey_company== "Speedway LLC"] <- "Speedway"
data$survey_company[data$survey_company== "Sherwin Williams"] <- "Sherwin-Williams"
data$survey_company[data$survey_company== "Shaw industries"] <- "Shaw Industries"
data$survey_company[data$survey_company== "Rsm"] <- "RSM"
data$survey_company[data$survey_company== "Robert W. Baird"] <- "Robert W Baird & Co."
data$survey_company[data$survey_company== "Reynolds and Reynold"] <- "Reynolds and Reynolds"
data$survey_company[data$survey_company== "QUICKEN LOANS"] <- "Quicken Loans"
data$survey_company[data$survey_company== "quicken loans"] <- "Quicken Loans"
data$survey_company[data$survey_company== "Quicken Loan"] <- "Quicken Loans"
data$survey_company[data$survey_company== "PWC Corporate Finance LLC"] <- "PwC"
data$survey_company[data$survey_company== "PwC Corporate Finance"] <- "PwC"
data$survey_company[data$survey_company== "PWC"] <- "PwC"
data$survey_company[data$survey_company== "Procter and Gamble"] <- "Procter & Gamble"
data$survey_company[data$survey_company== "Pricewaterhouse Coopers"] <- "PricewaterhouseCoopers"
data$survey_company[data$survey_company== "Polyone"] <- "PolyOne Corporation"
data$survey_company[data$survey_company== "PNC Financial Services"] <- "PNC Financial Services Group"
data$survey_company[data$survey_company== "PNC"] <- "PNC Bank"
data$survey_company[data$survey_company== "PHD"] <- "PHD Worldwide"
data$survey_company[data$survey_company== "PepsiCo-Frito Lay"] <- "PepsiCo Frito-Lay"
data$survey_company[data$survey_company== "Peoples Bank"] <- "Peoples Bancorp"
data$survey_company[data$survey_company== "Peloton Group Consulting"] <- "Peloton Consulting Group"
data$survey_company[data$survey_company== "Peloton Group"] <- "Peloton Consulting Group"
data$survey_company[data$survey_company== "Park Place Technologies"] <- "Park Place Technologies, Inc."
data$survey_company[data$survey_company== "Oracle NetSuite"] <- "Oracle Netsuite"
data$survey_company[data$survey_company== "Oracle - Netsuite"] <- "Oracle Netsuite"
data$survey_company[data$survey_company== "Oracle"] <- "Oracle Netsuite"
data$survey_company[data$survey_company== "Oppenheimer & Co Inc."] <- "Oppenheimer & Co. Inc."
data$survey_company[data$survey_company== "Northern Trust"] <- "Northern Trust Corporation"
data$survey_company[data$survey_company== "The Nielsen Company"] <- "Nielsen"
data$survey_company[data$survey_company== "news america Marketing"] <- "News America Marketing"
data$survey_company[data$survey_company== "NetSuite"] <- "Oracle Netsuite"
data$survey_company[data$survey_company== "Navistar, Inc"] <- "Navistar"
data$survey_company[data$survey_company== "Nationwide"] <- "Nationwide Insurance"
data$survey_company[data$survey_company== "Nations Lending"] <- "Nations Lending Corporation"
data$survey_company[data$survey_company== "Microsoft Corp"] <- "Microsoft"
data$survey_company[data$survey_company== "Medline Industries, Inc"] <- "Medline Industries Inc."
data$survey_company[data$survey_company== "McDonald's Corp."] <- "McDonald's Corporation"
data$survey_company[data$survey_company== "McDonald's"] <- "McDonald's Corporation"
data$survey_company[data$survey_company== "McAdams Financial"] <- "McAdam Financial"
data$survey_company[data$survey_company== "MartketVision Research"] <- "MarketVision Research"
data$survey_company[data$survey_company== "MarketVision"] <- "MarketVision Research"
data$survey_company[data$survey_company== "Marcum"] <- "Marcum LLP"
data$survey_company[data$survey_company== "Marathon Petroleum Corp"] <- "Marathon Petroleum Corporation"
data$survey_company[data$survey_company== "Macy's Credit and Customer Service Center"] <- "Macy's"
data$survey_company[data$survey_company== "Liberty Mutual"] <- "Liberty Mutual Insurance"
data$survey_company[data$survey_company== "LBrands- Bath & Body Works"] <- "LBrands"
data$survey_company[data$survey_company== "L Brands"] <- "LBrands"
data$survey_company[data$survey_company== "Kroger"] <- "Kroger Co."
data$survey_company[data$survey_company== "Kohl's Corporation"] <- "Kohl's"
data$survey_company[data$survey_company== "Kimberly-Clark Corporation"] <- "Kimberly-Clark"
data$survey_company[data$survey_company== "Kimberly Clark"] <- "Kimberly-Clark"
data$survey_company[data$survey_company== "Keyot Crew212"] <- "Keyot"
data$survey_company[data$survey_company== "Keyot Crew212"] <- "KEYOT"
data$survey_company[data$survey_company== "Keyence"] <- "Keyence Corporation"
data$survey_company[data$survey_company== "Key Bank"] <- "KeyBank"
data$survey_company[data$survey_company== "KeyBanc Capital Markets"] <- "KeyBank"
data$survey_company[data$survey_company== "KellyMitchell"] <- "KellyMitchell Group"
data$survey_company[data$survey_company== "JPMorgan Chase & Co."] <- "JP Morgan Chase"
data$survey_company[data$survey_company== "J.P. Morgan U.S. Private Bank"] <- "JP Morgan Chase"
data$survey_company[data$survey_company== "J.P. Morgan"] <- "JP Morgan Chase"
data$survey_company[data$survey_company== "J.P Morgan"] <- "JP Morgan Chase"
data$survey_company[data$survey_company== "JPMorgan Chase"] <- "JP Morgan Chase"
data$survey_company[data$survey_company== "JP Morgan and Chase"] <- "JP Morgan Chase"
data$survey_company[data$survey_company== "JP Morgan"] <- "JP Morgan Chase"
data$survey_company[data$survey_company== "Johnson & Johnson - DePuy Synthes"] <- "Johnson & Johnson"
data$survey_company[data$survey_company== "Johnson & Johnson - DePuy Synthes"] <- "Johnson & Johnson"
data$survey_company[data$survey_company== "Insight2Profit"] <- "Insight Enterprises"
data$survey_company[data$survey_company== "insight global"] <- "Insight Enterprises"
data$survey_company[data$survey_company== "Insight Global"] <- "Insight Enterprises"
data$survey_company[data$survey_company== "Insight2profit"] <- "Insight Enterprises"
data$survey_company[data$survey_company== "Insight"] <- "Insight Enterprises"
data$survey_company[data$survey_company== "IDK Yet"] <- "TBD"
data$survey_company[data$survey_company== "Huntington Bank"] <- "Huntington National Bank"
data$survey_company[data$survey_company== "Honda Manufacturing of America"] <- "Honda"
data$survey_company[data$survey_company== "Honda of America"] <- "Honda"
data$survey_company[data$survey_company== "Honda of America Manufacturing"] <- "Honda"
data$survey_company[data$survey_company== "Honda R&D Americas, Inc."] <- "Honda"
data$survey_company[data$survey_company== "hersheys"] <- "The Hershey Company"
data$survey_company[data$survey_company== "Hershey Entertainment & Resorts"] <- "The Hershey Company"
data$survey_company[data$survey_company== "Harrison Street"] <- "Harrison Street Real Estate Capital LLC"
data$survey_company[data$survey_company== "Guggenheim"] <- "Guggenheim Partners"
data$survey_company[data$survey_company== "Guggenheim Securities"] <- "Guggenheim Partners"
data$survey_company[data$survey_company== "GrubHub"] <- "Grubhub"
data$survey_company[data$survey_company== "Group Management Solutions"] <- "Group Management Services"
data$survey_company[data$survey_company== "Grant Thornton"] <- "Grant Thornton LLP"
data$survey_company[data$survey_company== "Grainger"] <- "Grainger Inc."
data$survey_company[data$survey_company== "Goodyear Tire & Rubber Co."] <- "Goodyear Tire & Rubber Company"
data$survey_company[data$survey_company== "Goodyear"] <- "Goodyear Tire & Rubber Company"
data$survey_company[data$survey_company== "Genral Motors"] <- "General Motors"
data$survey_company[data$survey_company== "GEICO"] <- "Geico"
data$survey_company[data$survey_company== "Frito-Lay"] <- "Frito Lay"
data$survey_company[data$survey_company== "frito lay"] <- "Frito Lay"
data$survey_company[data$survey_company== "Fisher investments"] <- "Fisher Investments"
data$survey_company[data$survey_company== "FIS (formerly Worldpay)"] <- "FIS"
data$survey_company[data$survey_company== "FIS Global"] <- "FIS"
data$survey_company[data$survey_company== "Fifth-Third Bank"] <- "Fifth Third Bank"
data$survey_company[data$survey_company== "Fidelity Investments"] <- "Fidelity"
data$survey_company[data$survey_company== "Ferguson Enterprises"] <- "Ferguson"
data$survey_company[data$survey_company== "Farmer"] <- "The Farmer Company"
data$survey_company[data$survey_company== "Express Corporate"] <- "Express"
data$survey_company[data$survey_company== "Ernst and Young"] <- "EY"
data$survey_company[data$survey_company== "Ernst & Young (EY)"] <- "EY"
data$survey_company[data$survey_company== "Ernst & Young"] <- "EY"
data$survey_company[data$survey_company== "Equity Methods"] <- "Equity Inc"
data$survey_company[data$survey_company== "EPIC"] <- "Epic"
data$survey_company[data$survey_company== "Epic Healthcare Systems"] <- "Epic"
data$survey_company[data$survey_company== "Epic Systems"] <- "Epic"
data$survey_company[data$survey_company== "Epic Systems Corporation"] <- "Epic"
data$survey_company[data$survey_company== "Emerson Commercial & Residential Solutions"] <- "Emerson"
data$survey_company[data$survey_company== "eli lilly and company"] <- "Eli Lilly and Company"
data$survey_company[data$survey_company== "Eli Lilly & Company"] <- "Eli Lilly and Company"
data$survey_company[data$survey_company== "Eli Lilly"] <- "Eli Lilly and Company"
data$survey_company[data$survey_company== "Echo Logistics"] <- "Echo Global Logistics"
data$survey_company[data$survey_company== "E & J Gallo Winery"] <- "E. & J. Gallo Winery"
data$survey_company[data$survey_company== "E&J Gallo"] <- "E. & J. Gallo Winery"
data$survey_company[data$survey_company== "E&J Gallo Winery"] <- "E. & J. Gallo Winery"
data$survey_company[data$survey_company== "Disney"] <- "The Walt Disney Company"
data$survey_company[data$survey_company== "DICK's Sporting Goods"] <- "DICK'S Sporting Goods"
data$survey_company[data$survey_company== "DHL"] <- "DHL Supply Chain"
data$survey_company[data$survey_company== "Deloitte Consulting"] <- "Deloitte"
data$survey_company[data$survey_company== "Deloitte LLP"] <- "Deloitte"
data$survey_company[data$survey_company== "Deloitte Tax"] <- "Deloitte"
data$survey_company[data$survey_company== "Deloitte, China"] <- "Deloitte"
data$survey_company[data$survey_company== "David J Joseph"] <- "David J. Joseph"
data$survey_company[data$survey_company== "Dauby, O'Connor & Zaleski"] <- "Dauby O'Connor & Zaleski"
data$survey_company[data$survey_company== "Cummins"] <- "Cummins, Inc."
data$survey_company[data$survey_company== "Crowe"] <- "Crowe LLP"
data$survey_company[data$survey_company== "CoyoteLogisitcs"] <- "Coyote Logistics"
data$survey_company[data$survey_company== "Coyote logistics"] <- "Coyote Logistics"
data$survey_company[data$survey_company== "Coyote"] <- "Coyote Logistics"
data$survey_company[data$survey_company== "Textron Aviation"] <- "Textron"
data$survey_company[data$survey_company== "Textron Specialized Vehicles"] <- "Textron"
data$survey_company[data$survey_company== "Textron Systems"] <- "Textron"
data$survey_company[data$survey_company== "Textron Systems: Lycoming Engines"] <- "Textron"
data$survey_company[data$survey_company== "Cowen"] <- "Cowen & Company"
data$survey_company[data$survey_company== "Cohen & Company"] <- "Cohen and Company"
data$survey_company[data$survey_company== "Cleveland cliffs"] <- "Cleveland Cliffs"
data$survey_company[data$survey_company== "Citi Bank"] <- "Citigroup"
data$survey_company[data$survey_company== "Cincinnati Insurance"] <- "Cincinnati Insurance Company"
data$survey_company[data$survey_company== "CIBC US"] <- "CIBC"
data$survey_company[data$survey_company== "Cengage Learning"] <- "Cengage"
data$survey_company[data$survey_company== "Cedar fair entertainment company"] <- "Cedar Fair Entertainment Company"
data$survey_company[data$survey_company== "Capital One"] <- "Capital Group"
data$survey_company[data$survey_company== "Capital One, Inc."] <- "Capital Group"
data$survey_company[data$survey_company== "Capgemini Invent"] <- "Capgemini"
data$survey_company[data$survey_company== "bswift"] <- "Bswift"
data$survey_company[data$survey_company== "Brown Gibbons Lang & Co"] <- "Brown Gibbons Lang & Co."
data$survey_company[data$survey_company== "BrightEdge Technologies"] <- "BrightEdge"
data$survey_company[data$survey_company== "BKD, LLP"] <- "BKD"
data$survey_company[data$survey_company== "BDO USA LLP"] <- "BDO"
data$survey_company[data$survey_company== "BDO USA"] <- "BDO"
data$survey_company[data$survey_company== "Baxter International"] <- "Baxter"
data$survey_company[data$survey_company== "Bath and Body Works"] <- "LBrands"
data$survey_company[data$survey_company== "Barclays Investment Bank"] <- "Barclays"
data$survey_company[data$survey_company== "Ayco, a Goldman Sachs Company"] <- "Ayco"
data$survey_company[data$survey_company== "Aon"] <- "AON"
data$survey_company[data$survey_company== "Ankura Consulting"] <- "Ankura"
data$survey_company[data$survey_company== "Andersen Tax"] <- "Andersen"
data$survey_company[data$survey_company== "Ameriprise Financial - Redstone Wealth Advisors"] <- "Ameriprise Financial Services"
data$survey_company[data$survey_company== "American Electric Power (AEP)"] <- "American Electric Power"
data$survey_company[data$survey_company== "American Eagle Outfitters"] <- "American Eagle"
data$survey_company[data$survey_company== "American Eagle Outfitters, Inc."] <- "American Eagle"
data$survey_company[data$survey_company== "Amazon Web Services"] <- "Amazon"
data$survey_company[data$survey_company== "Alvarez & Marsal"] <- "Alvarez and Marsal"
data$survey_company[data$survey_company== "AllianceBernstein"] <- "Alliance"
data$survey_company[data$survey_company== "Alliance Defending Freedom"] <- "Alliance"
data$survey_company[data$survey_company== "Alliance Data"] <- "Alliance"
data$survey_company[data$survey_company== "ALDI US"] <- "ALDI"
data$survey_company[data$survey_company== "ALDI USA"] <- "ALDI"
data$survey_company[data$survey_company== "Air Force Civilian Service"] <- "United States Air Force"
data$survey_company[data$survey_company== "Air Force Research Laboratory"] <- "United States Air Force"
data$survey_company[data$survey_company== "Abercrombie"] <- "Abercrombie & Fitch"
data$survey_company[data$survey_company== "Abbott Nutrition"] <- "Abbott"
data$survey_company[data$survey_company== "A J Gallagher"] <- "Arthur J. Gallagher"
data$survey_company[data$survey_company== "84.51"] <- "84.51ยบ"
data$survey_company[data$survey_company== "Bath & Body Works"] <- "LBrands"
data$survey_company[data$survey_company== "Brown Gibbons Lang & Company"] <- "Brown Gibbons Lang & Co."
data$survey_company[data$survey_company== "EJ Gallo"] <- "E. & J. Gallo Winery"
data$survey_company[data$survey_company== "KEYOT"] <- "Keyot"
data$survey_company[data$survey_company== "NielsenIQ"] <- "Nielsen"
data$survey_company[data$survey_company== "P&G"] <- "Procter & Gamble"
data$survey_company[data$survey_company== "Prudential Private Capital"] <- "Prudential Capital Group"
data$survey_company[data$survey_company== "Rubinbrown Advisors"] <- "RubinBrown LLP"
data$survey_company[data$survey_company== "Sun Trust Robinson Humphrey"] <- "Suntrust"
data$survey_company[data$survey_company== "Swagelok Company"] <- "Swagelok"
data$survey_company[data$survey_company== "The Reynolds and Reynolds Company"] <- "Reynolds and Reynolds"
data$survey_company[data$survey_company== "U.S. Air Force"] <- "United States Air Force"
```

## Clean Survey_GradSchool Variable

```{r}
data$survey_gradschool[data$survey_gradschool== "Boston Univeristy"] <- "Boston University"
data$survey_gradschool[data$survey_gradschool== "Boston University School of Law"] <- "Boston University"
data$survey_gradschool[data$survey_gradschool== "cornell university"] <- "Cornell University"
data$survey_gradschool[data$survey_gradschool== "have not chosen yet"] <- "NA"
data$survey_gradschool[data$survey_gradschool== "I haven't decided yet."] <- "NA"
data$survey_gradschool[data$survey_gradschool== "I haven't decided yet. :)"] <- "NA"
data$survey_gradschool[data$survey_gradschool== "king's college London"] <- "King's College London"
data$survey_gradschool[data$survey_gradschool== "N/a"] <- "NA"
data$survey_gradschool[data$survey_gradschool== "N/A"] <- "NA"
data$survey_gradschool[data$survey_gradschool== "New York university"] <- "New York University"
data$survey_gradschool[data$survey_gradschool== "No yet"] <- "NA"
data$survey_gradschool[data$survey_gradschool== "Northen Kentucky University Chase College of Law"] <- "Northern Kentucky University"
data$survey_gradschool[data$survey_gradschool== "not decided"] <- "NA"
data$survey_gradschool[data$survey_gradschool== "Not decided"] <- "NA"
data$survey_gradschool[data$survey_gradschool== "Not decided yet"] <- "NA"
data$survey_gradschool[data$survey_gradschool== "Not revive offers yet"] <- "NA"
data$survey_gradschool[data$survey_gradschool== "not sure"] <- "NA"
data$survey_gradschool[data$survey_gradschool== "Not sure, maybe NYU"] <- "NA"
data$survey_gradschool[data$survey_gradschool== "Ohio State"] <- "Ohio State University"
data$survey_gradschool[data$survey_gradschool== "Penn State School of Law"] <- "Penn State University"
data$survey_gradschool[data$survey_gradschool== "Rochester simon business school"] <- "University of Rochester"
data$survey_gradschool[data$survey_gradschool== "The Ohio State University"] <- "Ohio State University"
data$survey_gradschool[data$survey_gradschool== "Undecided"] <- "NA"
data$survey_gradschool[data$survey_gradschool== "Univeristy of Sanfrancisco"] <- "Univeristy of San Francisco"
data$survey_gradschool[data$survey_gradschool== "University of Cincinnati College of Law"] <- "University of Cincinnati"
data$survey_gradschool[data$survey_gradschool== "University of Illinois at Urbana Champaign"] <- "University of Illinois"
data$survey_gradschool[data$survey_gradschool== "University of Illinois at Urbana-Champaign"] <- "University of Illinois"
data$survey_gradschool[data$survey_gradschool== "University of leeds"] <- "University of Leeds"
data$survey_gradschool[data$survey_gradschool== "Univerty of Rochester"] <- "University of Rochester"
data$survey_gradschool[data$survey_gradschool== "Unsure"] <- "NA"
data$survey_gradschool[data$survey_gradschool== "Washington University in st. louis"] <- "Washington University in Saint Louis"
data$survey_gradschool[data$survey_gradschool== "Washinton University - St. Louis"] <- "Washington University in Saint Louis"
data$survey_gradschool[data$survey_gradschool== "Australia (unsure which school)"] <- "Unsure"
data$survey_gradschool[data$survey_gradschool== "New York university/ Northwest university"] <- "Unsure"
data$survey_gradschool[data$survey_gradschool== "Northwestern University or University of Michigan"] <- "Unsure"
data$survey_gradschool[data$survey_gradschool== "The University of Sydney or National university of Singapore or others"] <- "Unsure"
data$survey_gradschool[data$survey_gradschool== "Universities in UK/Singapore"] <- "Unsure"
data$survey_gradschool[data$survey_gradschool== "University of Illinois Urbana-Champaign"] <- "University of Illinois"
data$survey_gradschool[data$survey_gradschool== "University of Kansas Law School"] <- "University of Kansas"
data$survey_gradschool[data$survey_gradschool== "University of Leeds / Manchester University"] <- "Unsure"
data$survey_gradschool[data$survey_gradschool== "University of Melbourne or University of Rochester"] <- "Unsure"
data$survey_gradschool[data$survey_gradschool== "The University of Sydney"] <- "University of Sydney"
data$survey_gradschool[data$survey_gradschool== "Sydney University"] <- "University of Sydney"
data$survey_gradschool[data$survey_gradschool== "The University of Melbourne"] <- "University of Melbourne"
data$survey_gradschool[data$survey_gradschool== "The University of Sheffield"] <- "University of Sheffield"
data$survey_gradschool[data$survey_gradschool== "NYU - Bridge Program"] <- "New York University"
data$survey_gradschool[data$survey_gradschool== "NYU"] <- "New York University"
data$survey_gradschool[data$survey_gradschool== "NA"] <- "Unsure"
data$survey_gradschool[data$survey_gradschool== "LSU"] <- "Louisiana State University"
data$survey_gradschool[data$survey_gradschool== "KCL"] <- "King's College London"
data$survey_gradschool[data$survey_gradschool== "Embry riddle aeronautical university"] <- "Embry Riddle Aeronautical University"
data$survey_gradschool[data$survey_gradschool== "CWRU"] <- "Case Western Reserve University"
```

## Save as RDS

```{r}
saveRDS(data, file = "clean_data.rds")
```

